---
title: "Assay Report"
output: html_document
params:
  report: ""
---

# QC

between `r params$report$subsetMinNFeature$args[1]` and `r params$report$subsetMaxNFeature$args` features,
with a maximum of `r params$report$subsetPercent.mt$args` percent mitochondrial dna.

after applying the lower feature threshhold, we lose `r params$report$subsetMinNFeature$difference["cells"]` cells.
after applying the upper feature threshhold, we lose `r params$report$subsetMaxNFeature$difference["cells"]` cells.
after applying the mitochondrial threshhold, we lose `r params$report$subsetPercent.mt$difference["cells"]` cells.

## Before Filtering
```{r echo=FALSE}
library(patchwork)
library(ggplot2)
params$report$`plot::before.mito.vln`
# params$report$subsetMinNFeature
# params$report$subsetMinNFeature$comparison

# params$report$subsetMaxNFeature
# params$report$subsetMaxNFeature$comparison
# params$report$subsetMaxNFeature$difference
# params$report$subsetPercent.mt
# params$report$subsetPercent.mt$comparison
# params$report$subsetPercent.mt$difference
```


## After Filtering
lower feature threshhold
```{r echo = F}
```
upper feature threshhold
```{r echo = F}
cbind(c("upperFeatureThresh" = params$report$subsetMaxNFeature$difference, "lowerFeatureThresh" =params$report$subsetMinNFeature$difference , "Mitochondrial Upper Bound" = params$report$subsetPercent.mt$difference))

```
mitochondrial threshhold
```{r echo = F}

```

```{r echo = F}
params$report$`plot::afterThresh.vln`
```

# PCA 

## PCA
```{r echo = F}
params$report$`plot::dim.pca`
```

## Dimensions Loading, pc1, pc2
```{r echo = F}
params$report$`plot::dim.loadings`
params$report$`plot::elbow`
```

# Clustering

## counts
```{r echo = F }
params$report$`clusterCount`
```
```{r echo = F }
p = params$report$`plot::umap`
p$layers[[2]]$aes_params$size = 10
print(p)
params$report$`plot::tsne`
```