---
title: "Experiment Report"
output: html_document
params:
  seuratDir: ""
  clustermapDir: ""
---
```{r echo=F, out.width="25%", results='asis'}
library(data.tree)
library(purrr)
toName = function(f) substr(basename(f), 1, nchar(basename(f))-4)

# assayReports = Filter(function(f) endsWith(f, "report.rds"), list.files(params$seuratDir, full.names = T))
# names(assayReports) = lapply(assayReports, toName)
# assayReports = lapply(assayReports, readRDS)

# assayMarkers = Filter(function(f) endsWith(f, "markers.csv"), list.files(params$seuratDir, full.names = T))
# names(assayMarkers) = lapply(assayMarkers, toName)
# assayMarkers = lapply(assayMarkers, read.csv)

clustResults = Filter(function(f) endsWith(f, "results.csv"), list.files(params$clustermapDir, full.names = T))
names(clustResults) = lapply(clustResults, toName)
clustResults = lapply(clustResults, read.csv)

clustPics    = Filter(function(f) endsWith(f, ".png"), list.files(params$clustermapDir, recursive = T, full.names = T))
names(clustPics) <- lapply(clustPics, toName)
# clustPics = lapply(clustPics, function(pic) knitr::include_graphics(pic))
# print(clustPics)
# clustPics$d1.recolor.umap
# clustPics$d7.recolor.umap
umaps = Filter(function(x) endsWith(x,"umap"), names(clustPics)) %>% lapply(function(n) clustPics[[n]]) %>% unlist(recursive = T)
# params$clustermapDir
knitr::include_graphics(umaps)
knitr::kable(clustResults)
```


# QC Filtering

between `r params$report$subsetMinNFeature$args[1]` and `r params$report$subsetMaxNFeature$args` features,
with a maximum of `r params$report$subsetPercent.mt$args` percent mitochondrial dna.
We start with 
```{r echo=F}

rbind(lapply(params$reports, function(report) c(report$name, report$subsetMinNFeature$comparison[,1])))
```
after applying the lower feature threshhold, we lose `r params$report$subsetMinNFeature$difference["cells"]` cells.
after applying the upper feature threshhold, we lose `r params$report$subsetMaxNFeature$difference["cells"]` cells.
after applying the mitochondrial threshhold, we lose `r params$report$subsetPercent.mt$difference["cells"]` cells.

## Before Filtering
```{r echo=FALSE}
# library(patchwork)
# library(ggplot2)
params$report$`plot::before.mito.vln`
# params$report$subsetMinNFeature
# params$report$subsetMinNFeature$comparison

# params$report$subsetMaxNFeature
# params$report$subsetMaxNFeature$comparison
# params$report$subsetMaxNFeature$difference
# params$report$subsetPercent.mt
# params$report$subsetPercent.mt$comparison
# params$report$subsetPercent.mt$difference
```


## After Filtering
```{r echo = F}
params$report$`plot::afterThresh.vln`
```

we end with
```{r echo=F}
params$report$subsetPercent.mt$comparison[,1]
```

# PCA 

## PCA
```{r echo = F}
params$report$`plot::dim.pca`
```

## Dimensions Loading, pc1, pc2
```{r echo = F}
params$report$`plot::dim.loadings`
params$report$`plot::elbow`
```

# Clustering

## counts
```{r echo = F }
params$report$`clusterCount`
```
```{r echo = F }
p = params$report$`plot::umap`
p$layers[[2]]$aes_params$size = 10
print(p)
params$report$`plot::tsne`
```